\Large\bf Data Intensive processing with iRODS and the middleware CiGri for the Whisper project

### 2014-06-05 articles/2014/whisper/aricleEbauche/articleIrodsUserMeeting.tex
small change definition intuition correlation in data-intensive software part

The second package concerns correlations. 
Roughly speaking, a correlation is an operation with two seismograms (for a given time windows) that provides the coherent part of the two seismograms 
(associated to the 2 stations) which is the seismic wave that propagates between the 2 stations.
Moreover, it represents, in some favorables cases, a new virtual seismogram (it converges to the Green's function). Thus, the code computes all the correlations and provides an architecture of files that corresponds to all the couples of seismograms (for each date).

>>>>

The second package concerns correlations. 
Roughly speaking, a correlation is an operation with two seismograms (for a given time windows) that provides the coherent part of the two seismograms 
(associated to the 2 stations) which is the seismic waves that propagate between the 2 stations.
(Moreover, in some favorables cases, it converges to the Green's function). 
Thus, the code computes all the correlations and provides an architecture of files that corresponds to all the couples of seismograms (for each date).
